%-------------------------
% Resume in LaTeX
% Author: Maruti Mallinath Bandagar
% Tailored for: Full Stack Developer (MEAN Stack) - Codvo
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\input{glyphtounicode}

%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape \textbf{Maruti Mallinath Bandagar}} \\ \vspace{4pt}
    {\large Full-Stack Developer} \\ \vspace{6pt}
    \small
    \href{mailto:maruti.bandagar@yahoo.com}{\underline{maruti.bandagar@yahoo.com}} $|$
    +91 7755919112 $|$
    Pune, Maharashtra $|$
    \href{https://www.linkedin.com/in/marutibandagar/}{\underline{LinkedIn}} $|$
    \href{https://github.com/MarutiBandagar9121}{\underline{GitHub}}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
\small{
Results-driven Full-Stack Developer with \textasciitilde2 years of experience building scalable, high-performance web applications using Node.js, Express.js, TypeScript, PostgreSQL, MongoDB, and Redis. Proven ability to design and implement REST APIs with JWT/OAuth authentication, containerize services with Docker, and deploy on cloud platforms (GCP, AWS). Experienced in microservices architecture, CI/CD pipelines, and Agile (Scrum/Kanban) delivery. Passionate about clean, maintainable code and integrating emerging technologies---including AI/ML---to drive real business impact. Immediate Joiner.
}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Developer}{May 2024 -- Present}
      {Estatehub}{Pune, MH}
      \resumeItemListStart
        \resumeItem{\textbf{REST API Development:} Designed and developed robust REST APIs using Node.js and Express.js, implementing JWT/OAuth authentication and RBAC to secure enterprise-grade endpoints and ensure data integrity.}
        \resumeItem{\textbf{Microservices \& System Design:} Contributed to architectural decisions for microservices-based systems; built scalable, loosely coupled backend services with clear separation of concerns following MVC patterns.}
        \resumeItem{\textbf{Database Engineering:} Managed and optimized PostgreSQL and MongoDB databases; implemented Redis caching layers to reduce latency and improve throughput for high-traffic workloads.}
        \resumeItem{\textbf{Frontend Development:} Built responsive, maintainable frontends using React and TypeScript, applying HTML5, CSS3, and component-based architecture to deliver consistent cross-browser user experiences.}
        \resumeItem{\textbf{Cloud \& DevOps:} Established and managed cloud infrastructure on GCP and AWS; containerized applications using Docker ensuring 100\% environment consistency across development, staging, and production.}
        \resumeItem{\textbf{CI/CD \& Version Control:} Implemented and maintained CI/CD pipelines using GitHub Actions; enforced Git-based branching workflows and code review practices to support reliable, continuous delivery.}
        \resumeItem{\textbf{System Automation \& Integration:} Designed a dynamic document generation engine integrating third-party systems to produce customized PowerPoint and Excel reports; resolved critical bugs in payment gateway integrations, reducing transaction failures significantly.}
        \resumeItem{\textbf{Legacy Modernization \& ETL:} Led end-to-end migration of legacy codebases to current framework versions; executed large-scale ETL processes and web scraping pipelines to aggregate and prepare real estate data for downstream AI/ML training.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Savitribai Phule Pune University}{2021 -- 2024}
      {B.Sc. in Computer Science}{CGPA: 9.17}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{JobStream AI} $|$ \emph{Architect} $|$ \emph{Node.js, Express.js, PostgreSQL, Redis, Vector DB, Next.js}}{}
          \resumeItemListStart
            \resumeItem{Architected a distributed, microservices-based system using Python workers and a Next.js dashboard to handle high-volume asynchronous data ingestion, with Redis-backed caching for performance optimization.}
            \resumeItem{Implemented semantic search via Vector Databases (Qdrant), enabling natural language job discovery and demonstrating scalable, high-performance system design principles.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Lead Management System API} $|$ \emph{Developer} $|$ \emph{Node.js, Express.js, PostgreSQL, Redis, JWT}}{}
          \resumeItemListStart
            \resumeItem{Built a secure, high-performance REST API with Role-Based Access Control (RBAC) and JWT authentication, following MVC architecture for enterprise-level lead tracking and conversion monitoring.}
            \resumeItem{Integrated Redis caching and optimized PostgreSQL queries to ensure scalability and low-latency responses under high concurrent load.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Indian ID Validator (NPM Package)} $|$ \emph{Creator} $|$ \emph{Node.js, TypeScript}}{}
          \resumeItemListStart
            \resumeItem{Published an open-source TypeScript/Node.js library for Indian government ID validation on NPM, demonstrating high code quality standards, API design, and community contribution.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills \& Certifications}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Frontend:} React, Next.js, TypeScript, JavaScript (ES6+), HTML5, CSS3, Bootstrap \\[3pt]
     \textbf{Backend:} Node.js, Express.js, Python, Java (Spring Boot), PHP (Laravel) \\[3pt]
     \textbf{Databases \& Caching:} PostgreSQL, MongoDB, MySQL, Redis \\[3pt]
     \textbf{Architecture \& Patterns:} Microservices, REST APIs, MVC/MVVM, OAuth/JWT Authentication, RBAC \\[3pt]
     \textbf{Cloud \& DevOps:} AWS, GCP, Docker, CI/CD (GitHub Actions), Git, Containerization \\[3pt]
     \textbf{AI \& Data:} AI/ML Integration, LLMs, Vector Databases (Qdrant), ETL Pipelines, Web Scraping \\[3pt]
     \textbf{Methodologies:} Agile (Scrum/Kanban), Sprint Planning, Code Reviews, Technical Documentation \\[3pt]
     \textbf{Certifications:} Complete Web-Dev Bootcamp --- Udemy \quad $|$ \quad Programming for Everybody (Python) --- Coursera
    }}
 \end{itemize}

%-------------------------------------------
\end{document}