%-------------------------
% Resume in LaTeX
% Author: Maruti Mallinath Bandagar
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\input{glyphtounicode}

%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape \textbf{Maruti Mallinath Bandagar}} \\ \vspace{4pt}
    {\large Full-Stack Developer} \\ \vspace{6pt}
    \small
    \href{mailto:maruti.bandagar@yahoo.com}{\underline{maruti.bandagar@yahoo.com}} $|$
    +91 7755919112 $|$
    Pune, Maharashtra $|$
    \href{https://www.linkedin.com/in/marutibandagar/}{\underline{LinkedIn}} $|$
    \href{https://github.com/MarutiBandagar9121}{\underline{GitHub}}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
\small{
Immediate Joiner | Results-driven Full-Stack Developer with about 2 years of experience specializing in Python, Next.js, and AI Integration to build high-performance, user-centric applications. Highly versatile engineer with a proven track record in Java (Spring Boot), Node.js, and PHP (Laravel) environments. Expert at integrating AI features---including LLMs and Vector Databases---to achieve business goals, focusing on AI-driven automation, cloud scalability, and modernizing legacy systems to drive operational efficiency and ROI.
}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Developer}{ May 2024 -- Present}
      {Estatehub}{Pune, MH}
      \resumeItemListStart
        \resumeItem{\textbf{AI \& Machine Learning:} Prototyped an AI-powered thesis evaluation system, gaining hands-on experience with ML pipelines and integrating models to automate academic assessment.}
        \resumeItem{\textbf{Legacy Modernization:} Led the end-to-end migration of legacy codebases to current framework versions, restoring critical system functionality and improving long-term maintainability.}
        \resumeItem{\textbf{System Automation:} Designed and implemented a dynamic proposal generation engine, automating the creation of customized PowerPoint and Excel documents based on user specifications.}
        \resumeItem{\textbf{Cloud Infrastructure:} Established and managed the company's cloud infrastructure on GCP and AWS, optimizing service configurations for scalability and performance.}
        \resumeItem{\textbf{FinTech Reliability:} Resolved critical bugs in payment gateway integrations, significantly reducing transaction failures and improving financial data integrity.}
        \resumeItem{\textbf{Data Engineering:} Executed ETL processes for large-scale data migration and implemented web scraping solutions to aggregate real estate data for AI training.}
        \resumeItem{\textbf{Workflow Optimization:} Developed a comprehensive automated invoice management system for a plagiarism detection platform, handling generation, storage, and delivery.}
        \resumeItem{\textbf{Containerization:} Spearheaded the transition to Docker-based workflows, ensuring 100\% environment consistency across development, staging, and production.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Savitribai Phule Pune University}{2021 -- 2024}
      {B.Sc. in Computer Science}{CGPA: 9.17}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{JobStream AI} $|$ \emph{Architect}}{}
          \resumeItemListStart
            \resumeItem{Architected a distributed system using Python workers and a Next.js dashboard to handle high-volume data ingestion.}
            \resumeItem{Implemented semantic search via Vector DBs, allowing users to find job opportunities through natural language, directly improving platform engagement.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Indian ID Validator (NPM Package)} $|$ \emph{Creator}}{}
          \resumeItemListStart
            \resumeItem{Published an open-source library for government ID validation, demonstrating high-quality code standards and community leadership.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Lead Management System API} $|$ \emph{Developer}}{}
          \resumeItemListStart
            \resumeItem{Built a secure, high-performance API with RBAC and Redis caching to handle enterprise-level lead tracking and conversion monitoring.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------SKILLS & AWARDS-----------
\section{Skills \& Certifications}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Core Stack:} Python, Next.js, TypeScript, React \\[3pt]
     \textbf{Backend:} Java (Spring Boot), Node.js (Express), PHP (Laravel) \\[3pt]
     \textbf{Databases \& Search:} PostgreSQL, MySQL, MongoDB, Redis, Qdrant (Vector DB) \\[3pt]
     \textbf{Cloud \& DevOps:} AWS, GCP, Docker, CI/CD, Microservices Architecture \\[3pt]
     \textbf{Business Tools:} System Automation, Web Scraping, Financial Integration (Payment Gateways) \\[3pt]
     \textbf{Certifications:} Complete Web-Dev Bootcamp --- Udemy \quad $|$ \quad Programming for Everybody (Python) --- Coursera
    }}
 \end{itemize}

%-------------------------------------------
\end{document}